### 2018-04-15 tex/paper.tex
Added simplified escrow example to introduction; fixed multiple label problem.

This paper explores the design of a domain specific language, Marlowe,\footnote{Marlowe is named after Christopher Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury, which is also where our university is based. \url{https://en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{The code for Marlowe is available from \url{https://github.com/input-output-hk/scdsl}
} targetted at the execution of financial contracts in the style of Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is supported by IOHK.\footnote{\url{https://iohk.io}}
In doing this we are required to refine the model of contracts in a number of ways in order to fit with a radically different context.

In the traditional model, enforcement of the contract is the responsibility of the legal system; in the decentralised blockchain model, in which there is no central authority, the contract needs to be enforced by design. This means that we require participants to commit currency (or ``cash'' as we term it) to cover all possible expenditure in advance of the contract executing; we also have to use timeouts to ensure that the contract does not become stuck even if one or more of the participants stop interacting with it.

@@

The paper is structured like this: we begin in Section \ref{section:design} with a discussion of the design rationale for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe model, including the assumptions made in designing 
it, the types of the principal functions and a description of the DSL as an algebraic type, constructor by constructor. 
Section \ref{section:example} presents an example of a larger Marlowe contract, for incentivised saving, and Section 
\ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section \ref{section:next-steps} enumerates the next steps for the project.

@@

The DSL is modelled as an algebraic type in Haskell, together with an executable small-step semantics. 
We start by looking at the different types used by the model, then we look at the \haskellinline{Contract} DSL itself, and finally we give its semantics in Haskell. Section \ref{section:example} gives an example of Marlowe in action.

@@

\section{Incentivised saving}
\label{section:example}

@@

\section{Haskell embedding example}
\label{section:example}

@@

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know is not familiar with its syntax,
we have developed Meadow, a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of Meadow in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example}.

>>>>

This paper explores the design of a domain specific language, Marlowe,\footnote{Marlowe is named after Christopher Marlowe, the Elizabethan poet, dramatist and spy, who was born and educated in Canterbury, which is also where our university is based. \url{https://en.wikipedia.org/wiki/Christopher_Marlowe}}\footnote{The code for Marlowe is available from \url{https://github.com/input-output-hk/scdsl}
} targetted at the execution of financial contracts in the style of Peyton Jones, Eber and Seward~\cite{PeytonJones:2000} on blockchains. This work is a part of the Cardano project, and is supported by IOHK.\footnote{\url{https://iohk.io}}

In doing this we are required to refine the model of contracts in a number of ways in order to fit with a radically different context. Taking the following example of an ``escrow'' contract we can explain the differences more concretely. The aim of this contract, written in functional pseudocode in the style of~\cite{PeytonJones:2000} involves players 1, 2 and 3. Player 1 is to pay an amount of money to player 2 on receipt of goods. She pays the sum into escrow controlled by player 3. There are two options for the money: if two players agree to \haskellinline{pay} it goes ahead; if, on the other hand, two of the players opt to \haskellinline{refund} the money, that is done. The \haskellinline{When} construct ensures fires when its first argument -- a condition -- becomes true; the second argument, a \haskellinline{Contract} itself, is then performed, and this makes the payment according to the players' \haskellinline{Choice}.

\begin{haskellcode}
(When (Or (two_chose 1 2 3 refund)
          (two_chose 1 2 3 pay))
      (Choice (two_chose 1 2 3 pay)
              (Pay 1 2 AvailableMoney)
              redeem_original))
\end{haskellcode}

In the traditional model, enforcement of the contract is the responsibility of the legal system. If player 1 doesn't pay the money into escrow, or play 3 chooses to keep it for herself, then we can assume that they can be sued for the money and probably damages on top, thus providing both legal and financial incentives for compliance. On the other hand, in the decentralised blockchain model, where there is no central authority, the contract needs to be enforced by design.

This means that we require participants to commit money to cover all possible expenditure \emph{in advance of the contract executing}. In order to make sure that player continue to engage with a contract we ensure urgency by imposing timeouts: money is committed for a finite period, for example, and when waiting for a player to make a commitment we also impose a timeout to ensure that the contract does not become stuck even if one or more of the participants stops interacting with it.

@@

The paper is structured like this: we begin in Section \ref{section:design} with a discussion of the design rationale for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe model, including the assumptions made in designing 
it, the types of the principal functions and a description of the DSL as an algebraic type, constructor by constructor. 
Section \ref{section:example-saving} presents an example of a larger Marlowe contract, for incentivised saving. Section \ref{section:example-escrow} revisits the escrow example, and shows how it is described using a combination of Marlowe and Haskell constructs: that is, we use Marlowe as an embedded DSL. Section 
\ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section \ref{section:next-steps} enumerates the next steps for the project.

@@

The DSL is modelled as an algebraic type in Haskell, together with an executable small-step semantics. 
We start by looking at the different types used by the model, then we look at the \haskellinline{Contract} DSL itself, and finally we give its semantics in Haskell. Section \ref{section:example-saving} gives an example of Marlowe in action, and Section
\ref{section:example-escrow} shows the advantage of seeing Marlowe as a DSL embedded in Haskell.

@@

\section{Incentivised saving}
\label{section:example-saving}

@@

\section{Marlowe as a DSL embedded in Haskell}
\label{section:example-escrow}

@@

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know is not familiar with its syntax,
we have developed Meadow, a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of Meadow in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example-saving}.
